msc dissertation

### 2021-08-04 msc dissertation code.Rmd
latest

#conclude a sheet with only the relevant information 
#condition 1 = control; condition 2 = treatment

#Choose with the column position 
library("dplyr")
pennystudy2r1 <- pennycook2 %>% 
  select (c(1, 2, 3, 4, 57, 60, 250, 252, 284))

#re-code sharing intentions (fake/real) using the scale midpoint (1-3 = 0, 4-6 = 1)
pennystudy2r1$Fake[pennystudy2r1$Fake > 0 & pennystudy2r1$Fake < 4] <- 0
pennystudy2r1$Fake[pennystudy2r1$Fake > 3 & pennystudy2r1$Fake < 7] <- 1
pennystudy2r1$Fake

pennystudy2r1$Real[pennystudy2r1$Real > 0 & pennystudy2r1$Real < 4] <- 0
pennystudy2r1$Real[pennystudy2r1$Real > 3 & pennystudy2r1$Real < 7] <- 1
pennystudy2r1$Real

@@

#like the researcher did, change data frame from wide to long
##first drop unnecessary column
pennys2r1long <- subset(pennystudy2r1, select = c(1,2,3,4,10,14))

@@

keycol <- "newstype"
valuecol <- "measurement"
gathercols <- c("Fake","Real")

@@

pennys2r1long <- pennys2r1long[, c(1, 2, 6, 7, 4, 5, 3)]

@@

### attention check above and equal to 1
pennys2r1longa1 <- subset(pennys2r1long, dummycheck %in% c("1","2","3"))

### attention check above and equal to 2
pennys2r1longa2 <- subset(pennys2r1long, dummycheck %in% c("2","3"))

### attention check equal to 3
pennys2r1longa3 <- subset(pennys2r1long, dummycheck %in% c("3"))

@@

lm1 <- lm(veracity ~ newstype + newstype*condition, data = pennys2r1longa2)
summary(lm1)

@@

pennystudy2plot1 <- pennys2r1long %>%
  select (c(1, 2, 3, 4))

@@

p1 <- aggregate(measurement~condition+newstype, data = pennystudy2plot1, na.rm = TRUE, FUN = sum)
p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/428, 4)*100)))

##double check for correctness
sum(pennystudy2plot1$measurement,na.rm = TRUE)

#since the obs is 1712, thus 1712/2 = 856 participants. So to get percentage of sharing intention each fake and real news need to divided by 856/2 = 428
ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
```
### graph 2 attention check above and equal to 1

>>>>

#remove a participants that did not answer or fail to record any questions

pennycook2 <- pennycook2[!is.na(pennycook2$Fake),]

#data description: condition 1 = control; condition 2 = treatment

#Choose with the column position 
library("dplyr")
pennystudy2r1 <- pennycook2 %>% 
  select (c(1, 210, 211, 212, 213, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224, 225, 226, 227, 228, 229, 230, 231, 232, 233, 234, 235, 236, 237, 238, 239, 2, 3, 4, 57, 60, 250, 252, 284,))

#re-code sharing intentions (fake/real) using the scale midpoint (1-3 = 0, 4-6 = 1)

##Fake
pennystudy2r1$Fake[pennystudy2r1$Fake > 0 & pennystudy2r1$Fake < 4] <- 0
pennystudy2r1$Fake[pennystudy2r1$Fake > 3 & pennystudy2r1$Fake < 7] <- 1
pennystudy2r1$Fake

pennystudy2r1$Fake1_1[pennystudy2r1$Fake1_1 > 0 & pennystudy2r1$Fake1_1 < 4] <- 0
pennystudy2r1$Fake1_1[pennystudy2r1$Fake1_1 > 3 & pennystudy2r1$Fake1_1 < 7] <- 1

pennystudy2r1$Fake1_2[pennystudy2r1$Fake1_2 > 0 & pennystudy2r1$Fake1_2 < 4] <- 0
pennystudy2r1$Fake1_2[pennystudy2r1$Fake1_2 > 3 & pennystudy2r1$Fake1_2 < 7] <- 1

pennystudy2r1$Fake1_3[pennystudy2r1$Fake1_3 > 0 & pennystudy2r1$Fake1_3 < 4] <- 0
pennystudy2r1$Fake1_3[pennystudy2r1$Fake1_3 > 3 & pennystudy2r1$Fake1_3 < 7] <- 1

pennystudy2r1$Fake1_4[pennystudy2r1$Fake1_4 > 0 & pennystudy2r1$Fake1_4 < 4] <- 0
pennystudy2r1$Fake1_4[pennystudy2r1$Fake1_4 > 3 & pennystudy2r1$Fake1_4 < 7] <- 1

pennystudy2r1$Fake1_5[pennystudy2r1$Fake1_5 > 0 & pennystudy2r1$Fake1_5 < 4] <- 0
pennystudy2r1$Fake1_5[pennystudy2r1$Fake1_5 > 3 & pennystudy2r1$Fake1_5 < 7] <- 1

pennystudy2r1$Fake1_6[pennystudy2r1$Fake1_6 > 0 & pennystudy2r1$Fake1_6 < 4] <- 0
pennystudy2r1$Fake1_6[pennystudy2r1$Fake1_6 > 3 & pennystudy2r1$Fake1_6 < 7] <- 1

pennystudy2r1$Fake1_7[pennystudy2r1$Fake1_7 > 0 & pennystudy2r1$Fake1_7 < 4] <- 0
pennystudy2r1$Fake1_7[pennystudy2r1$Fake1_7 > 3 & pennystudy2r1$Fake1_7 < 7] <- 1

pennystudy2r1$Fake1_8[pennystudy2r1$Fake1_8 > 0 & pennystudy2r1$Fake1_8 < 4] <- 0
pennystudy2r1$Fake1_8[pennystudy2r1$Fake1_8 > 3 & pennystudy2r1$Fake1_8 < 7] <- 1

pennystudy2r1$Fake1_9[pennystudy2r1$Fake1_9 > 0 & pennystudy2r1$Fake1_9 < 4] <- 0
pennystudy2r1$Fake1_9[pennystudy2r1$Fake1_9 > 3 & pennystudy2r1$Fake1_9 < 7] <- 1

pennystudy2r1$Fake1_10[pennystudy2r1$Fake1_10 > 0 & pennystudy2r1$Fake1_10 < 4] <- 0
pennystudy2r1$Fake1_10[pennystudy2r1$Fake1_10 > 3 & pennystudy2r1$Fake1_10 < 7] <- 1

pennystudy2r1$Fake1_11[pennystudy2r1$Fake1_11 > 0 & pennystudy2r1$Fake1_11 < 4] <- 0
pennystudy2r1$Fake1_11[pennystudy2r1$Fake1_11 > 3 & pennystudy2r1$Fake1_11 < 7] <- 1

pennystudy2r1$Fake1_12[pennystudy2r1$Fake1_12 > 0 & pennystudy2r1$Fake1_12 < 4] <- 0
pennystudy2r1$Fake1_12[pennystudy2r1$Fake1_12 > 3 & pennystudy2r1$Fake1_12 < 7] <- 1

pennystudy2r1$Fake1_13[pennystudy2r1$Fake1_13 > 0 & pennystudy2r1$Fake1_13 < 4] <- 0
pennystudy2r1$Fake1_13[pennystudy2r1$Fake1_13 > 3 & pennystudy2r1$Fake1_13 < 7] <- 1

pennystudy2r1$Fake1_14[pennystudy2r1$Fake1_14 > 0 & pennystudy2r1$Fake1_14 < 4] <- 0
pennystudy2r1$Fake1_14[pennystudy2r1$Fake1_14 > 3 & pennystudy2r1$Fake1_14 < 7] <- 1

pennystudy2r1$Fake1_15[pennystudy2r1$Fake1_15 > 0 & pennystudy2r1$Fake1_15 < 4] <- 0
pennystudy2r1$Fake1_15[pennystudy2r1$Fake1_15 > 3 & pennystudy2r1$Fake1_15 < 7] <- 1

##Real
pennystudy2r1$Real[pennystudy2r1$Real > 0 & pennystudy2r1$Real < 4] <- 0
pennystudy2r1$Real[pennystudy2r1$Real > 3 & pennystudy2r1$Real < 7] <- 1
pennystudy2r1$Real

pennystudy2r1$Real1_1[pennystudy2r1$Real1_1 > 0 & pennystudy2r1$Real1_1 < 4] <- 0
pennystudy2r1$Real1_1[pennystudy2r1$Real1_1 > 3 & pennystudy2r1$Real1_1 < 7] <- 1

pennystudy2r1$Real1_2[pennystudy2r1$Real1_2 > 0 & pennystudy2r1$Real1_2 < 4] <- 0
pennystudy2r1$Real1_2[pennystudy2r1$Real1_2 > 3 & pennystudy2r1$Real1_2 < 7] <- 1

pennystudy2r1$Real1_3[pennystudy2r1$Real1_3 > 0 & pennystudy2r1$Real1_3 < 4] <- 0
pennystudy2r1$Real1_3[pennystudy2r1$Real1_3 > 3 & pennystudy2r1$Real1_3 < 7] <- 1

pennystudy2r1$Real1_4[pennystudy2r1$Real1_4 > 0 & pennystudy2r1$Real1_4 < 4] <- 0
pennystudy2r1$Real1_4[pennystudy2r1$Real1_4 > 3 & pennystudy2r1$Real1_4 < 7] <- 1

pennystudy2r1$Real1_5[pennystudy2r1$Real1_5 > 0 & pennystudy2r1$Real1_5 < 4] <- 0
pennystudy2r1$Real1_5[pennystudy2r1$Real1_5 > 3 & pennystudy2r1$Real1_5 < 7] <- 1

pennystudy2r1$Real1_6[pennystudy2r1$Real1_6 > 0 & pennystudy2r1$Real1_6 < 4] <- 0
pennystudy2r1$Real1_6[pennystudy2r1$Real1_6 > 3 & pennystudy2r1$Real1_6 < 7] <- 1

pennystudy2r1$Real1_7[pennystudy2r1$Real1_7 > 0 & pennystudy2r1$Real1_7 < 4] <- 0
pennystudy2r1$Real1_7[pennystudy2r1$Real1_7 > 3 & pennystudy2r1$Real1_7 < 7] <- 1

pennystudy2r1$Real1_8[pennystudy2r1$Real1_8 > 0 & pennystudy2r1$Real1_8 < 4] <- 0
pennystudy2r1$Real1_8[pennystudy2r1$Real1_8 > 3 & pennystudy2r1$Real1_8 < 7] <- 1

pennystudy2r1$Real1_9[pennystudy2r1$Real1_9 > 0 & pennystudy2r1$Real1_9 < 4] <- 0
pennystudy2r1$Real1_9[pennystudy2r1$Real1_9 > 3 & pennystudy2r1$Real1_9 < 7] <- 1

pennystudy2r1$Real1_10[pennystudy2r1$Real1_10 > 0 & pennystudy2r1$Real1_10 < 4] <- 0
pennystudy2r1$Real1_10[pennystudy2r1$Real1_10 > 3 & pennystudy2r1$Real1_10 < 7] <- 1

pennystudy2r1$Real1_11[pennystudy2r1$Real1_11 > 0 & pennystudy2r1$Real1_11 < 4] <- 0
pennystudy2r1$Real1_11[pennystudy2r1$Real1_11 > 3 & pennystudy2r1$Real1_11 < 7] <- 1

pennystudy2r1$Real1_12[pennystudy2r1$Real1_12 > 0 & pennystudy2r1$Real1_12 < 4] <- 0
pennystudy2r1$Real1_12[pennystudy2r1$Real1_12 > 3 & pennystudy2r1$Real1_12 < 7] <- 1

pennystudy2r1$Real1_13[pennystudy2r1$Real1_13 > 0 & pennystudy2r1$Real1_13 < 4] <- 0
pennystudy2r1$Real1_13[pennystudy2r1$Real1_13 > 3 & pennystudy2r1$Real1_13 < 7] <- 1

pennystudy2r1$Real1_14[pennystudy2r1$Real1_14 > 0 & pennystudy2r1$Real1_14 < 4] <- 0
pennystudy2r1$Real1_14[pennystudy2r1$Real1_14 > 3 & pennystudy2r1$Real1_14 < 7] <- 1

pennystudy2r1$Real1_15[pennystudy2r1$Real1_15 > 0 & pennystudy2r1$Real1_15 < 4] <- 0
pennystudy2r1$Real1_15[pennystudy2r1$Real1_15 > 3 & pennystudy2r1$Real1_15 < 7] <- 1

@@

#like the researcher did, change data frame from wide to long
##first drop unnecessary column
colnames(pennystudy2r1)

pennys2r1long <- subset(pennystudy2r1, select = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,40,44))

@@

keycol <- "newstype"
valuecol <- "measurement"
gathercols <- c("Fake1_1","Fake1_2","Fake1_3","Fake1_4","Fake1_5","Fake1_6","Fake1_7","Fake1_8","Fake1_9","Fake1_10","Fake1_11","Fake1_12","Fake1_13","Fake1_14","Fake1_15","Real1_1","Real1_2","Real1_3","Real1_4","Real1_5","Real1_6","Real1_7","Real1_8","Real1_9","Real1_10","Real1_11","Real1_12","Real1_13","Real1_14","Real1_15")

@@

pennys2r1long <- pennys2r1long[, c(1, 2, 8, 9, 7, 4, 3, 6, 5)]

##rename real and fake to avereal and avefake, change dummycheck to attentioncheck to make it clear

names(pennys2r1long)[6] <- "Real_ave"
names(pennys2r1long)[7] <- "Fake_ave"
names(pennys2r1long)[5] <- "attentioncheck"

##create a headline veracity column, fake news items code as 0, real news items code as 1

pennys2r1long <- pennys2r1long %>%
  mutate(headlineveracity = case_when(
    startsWith(newstype, "R") ~ "1",
    startsWith(newstype, "F") ~ "0"
    ))

##realise that original researcher exclude the observation with answer contains na, thus the obs needs to minus 23 to match original obs 25,627

pennys2r1long_nona <- pennys2r1long[!is.na(pennys2r1long$measurement),]

@@

### attention check above and equal to 1
pennys2r1longa1 <- subset(pennys2r1long, attentioncheck %in% c("1","2","3"))

### attention check above and equal to 2
pennys2r1longa2 <- subset(pennys2r1long, attentioncheck %in% c("2","3"))

### attention check equal to 3
pennys2r1longa3 <- subset(pennys2r1long, attentioncheck %in% c("3"))

###find out the number of participants for each attention check
attention1 <- subset(pennystudy2r1, dummycheck %in% c("1","2","3"))
attention2 <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
attention3 <- subset(pennystudy2r1, dummycheck %in% c("3"))
```

@@

lm1 <- lm(measurement ~ headlineveracity + headlineveracity*condition, data = pennys2r1long_nona)
summary(lm1)

@@

@@

p1 <- aggregate(measurement~condition+headlineveracity, data = pennys2r1long_nona, na.rm = TRUE, FUN = sum)

#since the obs is 25,627, thus for each news in each condition, it observed 25,627/4 = 6406.75
p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/6406.75, 4)*100)))

#plot the graph

ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = headlineveracity)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
```
### graph 2 attention check above and equal to 1
